Comb associative operads

### 2018-08-23 Article.tex
Rédaction première partie opérades magmatiques
Debut 1re section
Partie 1 (chantier)
Partie 1 chantier (suite)
Remarques de Cyrille sur partie 1
Modification algo de Buchberger
Harmonisation 3 premières sections
Ajout mini-intro section comb associative operads
Modifications
Petites modifs
Relecture partie 2
Modifications après relecture des deux premières sections
Quotients de Mag 3
Modifs
Ajout MSC
Reorganisation derniere partie
Rédaction abstract

% Author: Cyrille Chenavier, Christophe Cordero, Samuele Giraudo
% Creation: may. 2018
% Modifications: may. 2018, june 2018

@@

% Tikz.
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathmorphing}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Comb associative operads}
\keywords{Operad; trees; Rewrite rule; Presentation; Enumeration.}
\subjclass[2010]{\Todo{}}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

@@

\newcommand{\Oca}{\mathcal{O}}
\newcommand{\Rfr}{\mathfrak{r}}
\newcommand{\Sfr}{\mathfrak{s}}
\newcommand{\Tfr}{\mathfrak{t}}

\newcommand{\Zero}{\mathtt{0}}
\newcommand{\Two}{\mathtt{2}}
\newcommand{\HilbertSeries}{\mathcal{H}}
\newcommand{\GeneratingSet}{\mathfrak{G}}
\newcommand{\FreeOperad}{\mathrm{F}}
\newcommand{\Mag}{\mathsf{Mag}}
\newcommand{\As}{\mathsf{As}}
\newcommand{\CAs}[1]{\mathsf{CAs}^{(#1)}}
\newcommand{\CAsAll}{\mathbf{CAs}}
\newcommand{\PrefixWord}{\mathrm{p}}
\newcommand{\Deg}{\mathrm{deg}}
\newcommand{\LComb}[1]{\mathfrak{c}^{(#1)}_{\diagup}}
\newcommand{\RComb}[1]{\mathfrak{c}^{(#1)}_{\diagdown}}
\newcommand{\LBranch}{\mathrm{lb}}
\newcommand{\RBranch}{\mathrm{rb}}
\newcommand{\Catalan}{\mathrm{cat}}
\newcommand{\OrdCAs}{\preceq}

\DeclareMathOperator{\Product}{\star}
\DeclareMathOperator{\Congr}{\equiv}
\DeclareMathOperator{\Rew}{\to}
\DeclareMathOperator{\RewRT}{\overset{*}{\Rew}}
\DeclareMathOperator{\RewT}{\overset{+}{\Rew}}
\DeclareMathOperator{\RewRTS}{\overset{*}{\leftrightarrow}}
\DeclareMathOperator{\RewContext}{\Rightarrow}
\DeclareMathOperator{\RewContextRT}{\overset{*}{\RewContext}}
\DeclareMathOperator{\RewContextT}{\overset{+}{\RewContext}}
\DeclareMathOperator{\lcm}{lcm}

@@

% Tree drawings.
\tikzstyle{Node}=[circle,draw=Col1!80,fill=Col1!8,inner sep=1pt,
minimum size=2mm,thick,font=\scriptsize]
\tikzstyle{Edge}=[draw=Col2!80,cap=round,thick]
\tikzstyle{Leaf}=[rectangle,draw=ColBlack!70,fill=ColBlack!16,
inner sep=0pt,minimum size=1mm,thick]
\tikzstyle{NodeST}=[font=\footnotesize]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    The associative operad is the quotient of the magmatic operad by
    the operad congruence identifying the two binary trees of degree
    $2$. We introduce here a generalization of the associative operad
    depending on a nonnegative integer $d$, called $d$-comb associative
    operad, as the quotient of the magmatic operad by the operad
    congruence identifying the left and the right comb binary trees of
    degree $d$. We study the case $d = 3$ and provide an orientation
    of its space of relations by using rewrite systems on trees and
    the Buchberger algorithm for operads to obtain a convergent
    rewrite system.
\end{abstract}

@@

>>>>

% Author: Cyrille Chenavier, Christophe Cordero, Samuele Giraudo
% Creation: may. 2018
% Modifications: may. 2018, june 2018, july 2018, aug. 2018

@@

% Tikz.
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}

@@

% Mathematical symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Comb associative operads}
\keywords{Operad; trees; Rewrite rule; Presentation; Enumeration.}
\subjclass[2010]{18D50, 68Q42, 05C05.}
\date{\today}
\author{Cyrille Chenavier \and Christophe Cordero \and Samuele Giraudo}
\address{\scriptsize Université Paris-Est, LIGM (UMR $8049$), CNRS,
    ENPC, ESIEE Paris, UPEM, F-$77454$, Marne-la-Vallée, France}
\email{cyrille.chenavier@u-pem.fr}
\email{christophe.cordero@u-pem.fr}
\email{samuele.giraudo@u-pem.fr}

@@

\newcommand{\Angle}[1]{\left\langle#1\right\rangle}

\newcommand{\Oca}{\mathcal{O}}
\newcommand{\Afr}{\mathfrak{a}}
\newcommand{\Rfr}{\mathfrak{r}}
\newcommand{\Sfr}{\mathfrak{s}}
\newcommand{\Tfr}{\mathfrak{t}}
\newcommand{\BranchingTrees}{\mathfrak{P}}

\newcommand{\Zero}{\mathtt{0}}
\newcommand{\Two}{\mathtt{2}}
\newcommand{\HilbertSeries}{\mathcal{H}}
\newcommand{\GeneratingSet}{\mathfrak{G}}
\newcommand{\FreeOperad}{\mathrm{F}}
\newcommand{\Mag}{\mathsf{Mag}}
\newcommand{\KMag}{\K \Angle{\Mag}}
\newcommand{\QMag}{\mathcal{Q}\left(\KMag\right)}
\newcommand{\IMag}{\mathcal{I}\left(\KMag\right)}
\newcommand{\As}{\mathsf{As}}
\newcommand{\CAs}[1]{\mathsf{CAs}^{\left(#1\right)}}
\newcommand{\CAsAll}{\mathbf{CAs}}
\newcommand{\KCAs}[1]{\K\CAs{#1}}
\newcommand{\KCAsAll}{\K\CAsAll}
\newcommand{\PrefixWord}{\mathrm{p}}
\newcommand{\Deg}{\mathrm{deg}}
\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagup}}
\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagdown}}
\newcommand{\LRank}{\mathrm{lr}}
\newcommand{\RBranch}{\mathrm{rb}}
\newcommand{\Catalan}{\mathrm{cat}}
\newcommand{\OrdQMag}{\preceq_{\mathrm{incl}}}
\newcommand{\InfQMag}{\wedge_{\mathrm{incl}}}
\newcommand{\SupQMag}{\vee_{\mathrm{incl}}}
\newcommand{\LatQMag}{\left(\QMag,\OrdQMag,\InfQMag,\SupQMag\right)}
\newcommand{\OrdCAs}{\preceq_{\mathrm{div}}}
\newcommand{\InfCAs}{\wedge_{\mathrm{div}}}
\newcommand{\SupCAs}{\vee_{\mathrm{div}}}
\newcommand{\LatCAs}{\left(\CAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\LatKCAs}{\left(\KCAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\Unit}{\mathds{1}}
\newcommand{\Leaf}{\perp}
\newcommand{\Corolla}{\mathrm{c}}
\newcommand{\NormalForms}{\mathfrak{N}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Compositions}{\mathcal{C}}

\DeclareMathOperator{\Product}{\star}
\DeclareMathOperator{\Congr}{\equiv}
\DeclareMathOperator{\Rew}{\to}
\DeclareMathOperator{\RewRT}{\overset{*}{\Rew}}
\DeclareMathOperator{\RewT}{\overset{+}{\Rew}}
\DeclareMathOperator{\RewRTS}{\overset{*}{\leftrightarrow}}
\DeclareMathOperator{\RewContext}{\Rightarrow}
\DeclareMathOperator{\RewContextT}{\overset{+}{\RewContext}}
\DeclareMathOperator{\RewContextRT}{\overset{\ast}{\RewContext}}
\DeclareMathOperator{\RewContextRST}{\overset{\ast}{\Leftrightarrow}}
\DeclareMathOperator{\lcm}{lcm}

@@

\newcommand{\Lightning}[1]{
\mathfrak{c}^{(#1)}_{\begin{tikzpicture}[scale=.1, Centering]
    \draw (0,0)--(-1,-2);
    \draw (-1,-2)--(0,-2);
    \draw (0,-2)--(-1,-4);
\end{tikzpicture}}}

% Tizk styles.
\tikzstyle{Node}=[circle,draw=Col1!80,fill=Col1!8,inner sep=1pt,
minimum size=2mm,thick,font=\scriptsize]
\tikzstyle{Edge}=[draw=Col2!80,cap=round,thick]
\tikzstyle{EdgeColorF}=[Edge,draw=Col6!90,ultra thick]
\tikzstyle{Leaf}=[rectangle,draw=ColBlack!70,fill=ColBlack!16,
inner sep=0pt,minimum size=1mm,thick]
\tikzstyle{NodeST}=[font=\footnotesize]
\tikzstyle{Injection}=[ColBlack!100,draw,
{>[scale=1.5,length=4,width=5]}-{>[scale=1.5,length=4,width=5]}]
\tikzstyle{Map}=[ColBlack!100,draw,-{>[scale=1.5,length=4,width=5]}]

% Tree drawings.

\newcommand{\TreeA}{
\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
    \node(0)at(0.00,-5.25){};
    \node(2)at(2.00,-5.25){};
    \node(4)at(4.00,-3.50){};
    \node(6)at(6.00,-1.75){};
    \node[NodeST](1)at(1.00,-3.50){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](3)--(5);
    \draw[Edge](4)--(3);
    \draw[Edge](6)--(5);
    \node(r)at(5.00,1.31){};
    \draw[Edge](r)--(5);
\end{tikzpicture}}

\newcommand{\TreeB}{
\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
    \node(0)at(0.00,-3.50){};
    \node(2)at(2.00,-5.25){};
    \node(4)at(4.00,-5.25){};
    \node(6)at(6.00,-1.75){};
    \node[NodeST](1)at(1.00,-1.75){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,-3.50){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(5.00,0.00){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(5);
    \draw[Edge](2)--(3);
    \draw[Edge](3)--(1);
    \draw[Edge](4)--(3);
    \draw[Edge](6)--(5);
    \node(r)at(5.00,1.31){};
    \draw[Edge](r)--(5);
\end{tikzpicture}}

\newcommand{\TreeC}{
\begin{tikzpicture}[xscale=.22,yscale=.18,Centering]
    \node(0)at(0.00,-4.67){};
    \node(2)at(2.00,-4.67){};
    \node(4)at(4.00,-4.67){};
    \node(6)at(6.00,-4.67){};
    \node[NodeST](1)at(1.00,-2.33){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(5.00,-2.33){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](1)--(3);
    \draw[Edge](2)--(1);
    \draw[Edge](4)--(5);
    \draw[Edge](5)--(3);
    \draw[Edge](6)--(5);
    \node(r)at(3.00,1.75){};
    \draw[Edge](r)--(3);
\end{tikzpicture}}

\newcommand{\TreeD}{
\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
    \node(0)at(0.00,-1.75){};
    \node(2)at(2.00,-5.25){};
    \node(4)at(4.00,-5.25){};
    \node(6)at(6.00,-3.50){};
    \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,-3.50){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(5.00,-1.75){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](2)--(3);
    \draw[Edge](3)--(5);
    \draw[Edge](4)--(3);
    \draw[Edge](5)--(1);
    \draw[Edge](6)--(5);
    \node(r)at(1.00,1.31){};
    \draw[Edge](r)--(1);
\end{tikzpicture}}

\newcommand{\TreeE}{
\begin{tikzpicture}[xscale=.22,yscale=.23,Centering]
    \node(0)at(0.00,-1.75){};
    \node(2)at(2.00,-3.50){};
    \node(4)at(4.00,-5.25){};
    \node(6)at(6.00,-5.25){};
    \node[NodeST](1)at(1.00,0.00){\begin{math}\Product\end{math}};
    \node[NodeST](3)at(3.00,-1.75){\begin{math}\Product\end{math}};
    \node[NodeST](5)at(5.00,-3.50){\begin{math}\Product\end{math}};
    \draw[Edge](0)--(1);
    \draw[Edge](2)--(3);
    \draw[Edge](3)--(1);
    \draw[Edge](4)--(5);
    \draw[Edge](5)--(3);
    \draw[Edge](6)--(5);
    \node(r)at(1.00,1.31){};
    \draw[Edge](r)--(1);
\end{tikzpicture}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We study quotients of the magmatic operad, that is the free
  nonsymmetric operad over one binary generator. In the linear setting,
  we show that the set of these quotients admits a lattice structure and
  we show the Grassmann formula for this lattice. In the nonlinear
  setting, we define comb associative operads, indexed by nonegative
  integres, as generalizations of the associative operad. We show that
  the set of comb associative operads admits a lattice structure,
  isomoprhic to the lattice of nonnegative integers equipped with the
  division order, and we provide a finite convergent presentation for the
  comb associative operad corresponding to $3$. Finally, we study
  quotients of the magmatic operad by one relation of degree $3$ by
  studying their Hilbert series and providing combinarotial realizations.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Magmatic_quotient_three}

### 2018-08-23 Introduction.tex
Rédaction abstract

This text is presented as follows. Section~\ref{sec:operad_Mag} contains
preliminaries about operads, binary trees, the magmatic operad, and
rewrite systems on binary trees. We also prove and recall some important
lemmas about rewrite systems on trees used thereafter. In
Section~\ref{sec:Magmatic_operads}, we study the set of all the
quotients of $\Mag$ seen as an operad in the category of sets and its
lattice structure. Section~\ref{sec:CAs_d} is the heart of this article
and is devoted to the study of the comb associative operads
$\CAs{\gamma}$. Finally, Section~\ref{sec:MAg_3} presents our results
about the quotients of $\Mag$ obtained by equating two trees of
degree~$3$.
\medbreak

>>>>

This text is presented as follows. Section~\ref{sec:operad_Mag} contains
preliminaries about operads, binary trees, the magmatic operad, and
rewrite systems on binary trees. We also prove and recall some important
lemmas about rewrite systems on trees used thereafter. In
Section~\ref{sec:Magmatic_operads}, we study the set of all the
quotients of $\Mag$ seen as an operad in the category of vector spaces
and its lattice structure. Section~\ref{sec:CAs_d} is the heart of this
article and is devoted to the study of the comb associative operads
$\CAs{\gamma}$. Finally, Section~\ref{sec:MAg_3} presents our results
about the quotients of $\Mag$ obtained by equating two trees of
degree~$3$.
\medbreak
